The Power of Dependent Reflection

### 2021-07-05 paper.tex
Introduce PostScript (section 2).
Abstact polishing [take 1]

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}

  In this paper we explore a way to write correct by construction
  programs in languages that do not have built-in verification
  capabilities.  This is achieved in three steps.  Firstly, we
  shallowly embed the language (or its subset) inside of a
  dependently-typed system.  Secondly, we write a program
  within that embedding using dependent types to guarantee
  a property of interest.  Thirdly, we provide a way to
  translate the embedded program back into the original language,
  \eg{} so that it can be used by the existing compilers.

  The main focus of the paper is the third step, which we
  call \emph{extraction}.  The main insight of the paper is
  the use of reflection mechanism of a dependently-typed language
  to achieve extraction.  As a result, the embedding, the
  program and the extractor are written in a single language.

  To demonstrate these ideas precisely we embed a subset of
  the PostScript language in Agda and explain all the three
  steps.

@@

% Agda Basics and Extraction
\input{latex/background}

% PostScript Language and its embedding
\section{PostScript and its embedding in Agda}
Demonstrate a few examples.

>>>>

\usepackage{epsf}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  This paper proposes a novel tecnhique to write correct by construction
  programs in languages that do not have built-in verification
  capabilities.  This is achieved in three steps.  Firstly, we
  shallowly embed the language (or its subset) into a
  dependently-typed system.  Secondly, we write a program
  in that embedding, and we use dependent types to guarantee
  correctness properties of interest.  Thirdly, we
  translate the embedded program back into the original language,
  so that it can be used by the existing compilers and tools.

  The main insight of the paper is the observation that de\-pen\-den\-tly-typed
  languages that are equipped with reflection mecahnisms make it possible
  to expres all the three steps in a single language.  Essentially,
  this allows us to express programs, its formal properties and
  compilers hand-in-hand, offering a lot of flexibility to programmers.

  To demonstrate the approach precisely, we embed a subset of
  the PostScript language in Agda.  We explain all the three
  steps, illustrating them with several short examples.

@@

% Agda Basics and Extraction
\input{latex/background}
\input{latex/psembedding}
